---
title: "House Price Data"
output: html_document
---

```{r}
train <- read.csv("C:/Users/SAROJ/Desktop/House Price/train.csv")
```

#Separating the factors and the numeric columns

```{r}
names(train)[sapply(train, is.numeric)]->n
train_num = train[,n]
names(train)[sapply(train, is.factor)]->f
train_fac = train[,f]
names(train_num)
```

#Features to be converted to factors

```{r}
n_to_f = c("BsmtFullBath","BsmtHalfBath","FullBath","HalfBath","BedroomAbvGr","KitchenAbvGr","TotRmsAbvGrd","Fireplaces","MoSold","YrSold")
```

```{r}
train_fac_2 = train_num[,n_to_f]
```

```{r}
apply(train_fac_2,2,as.factor)->a
as.data.frame(a)->b
```

```{r}
factors = data.frame(train_fac,b)
```



#Way too many NAs

```{r}
#remove alley,pool quality,MiscFeature
factors[,-c(3,39,41)]->factors
```

#Feature Correction

```{r}
as.character(factors$BsmtQual)->factors$BsmtQual
as.character(factors$BsmtCond)->factors$BsmtCond
as.character(factors$BsmtExposure)->factors$BsmtExposure
as.character(factors$BsmtFinType1)->factors$BsmtFinType1
as.character(factors$BsmtFinType2)->factors$BsmtFinType2

factors$BsmtQual[is.na(factors$BsmtQual)]="No Basement"
factors$BsmtCond[is.na(factors$BsmtCond)]="No Basement"
factors$BsmtExposure[is.na(factors$BsmtExposure)]="No Basement"
factors$BsmtFinType1[is.na(factors$BsmtFinType1)]="No Basement"
factors$BsmtFinType2[is.na(factors$BsmtFinType2)]="No Basement"

as.factor(factors$BsmtQual)->factors$BsmtQual
as.factor(factors$BsmtCond)->factors$BsmtCond
as.factor(factors$BsmtExposure)->factors$BsmtExposure
as.factor(factors$BsmtFinType1)->factors$BsmtFinType1
as.factor(factors$BsmtFinType2)->factors$BsmtFinType2

```

```{r}

as.character(factors$GarageCond)->factors$GarageCond
as.character(factors$GarageQual)->factors$GarageQual
as.character(factors$GarageFinish)->factors$GarageFinish
as.character(factors$GarageType)->factors$GarageType


factors$GarageQual[is.na(factors$GarageQual)]="No Garage"
factors$GarageCond[is.na(factors$GarageCond)]="No Garage"
factors$GarageFinish[is.na(factors$GarageFinish)]="No Garage"
factors$GarageType[is.na(factors$GarageType)]="No Garage"


as.factor(factors$GarageQual)->factors$GarageQual
as.factor(factors$GarageCond)->factors$GarageCond
as.factor(factors$GarageFinish)->factors$GarageFinish
as.factor(factors$GarageType)->factors$GarageType
```

```{r}
as.character(factors$Fence)->factors$Fence
factors$Fence[is.na(factors$Fence)]="No Fence"
as.factor(factors$Fence)->factors$Fence
as.character(factors$FireplaceQu)->factors$FireplaceQu
factors$FireplaceQu[is.na(factors$FireplaceQu)]="No Fireplace"
as.factor(factors$FireplaceQu)->factors$FireplaceQu
```

```{r}

summary(factors)
```

#Data Imputation

```{r}
mice(data = factors, m = 2, method = "polyreg", maxit = 3, seed = 500)->imputed_f
```

```{r}
factors=complete(imputed_f,2)

```

```{r}
summary(factors)
```

#Numeric Attributes

```{r}
names(train) %in% names(factors)->res
```

```{r}
vec = c()
k=1
for (i in 1:length(res)) {
if(res[i]==FALSE)
{
  vec[k]=i
  k=k+1
}
}
```

```{r}
train_num = train[,vec]
```

```{r}
colnames(train_num)
```

```{r}
#remove alley,pool quality,MiscFeature
train_num[,-c(5,28,29)]->train_num
```

```{r}

```
```{r}
mice(data = train_num, m = 2, method = "pmm", maxit = 5, seed = 500)->imputed_n
```
```{r}
train_num=complete(imputed_n,2)
```

```{r}
#Remove ID column
train_num = train_num[,-1]
```


maybe : 
BsmtFinSF1:
TotalBsmtSF:
1stFlrSF: 
GrLivArea:
OpenPorchSF:    


non:
BsmtFinSF2: 
LowQualFinSF:
EnclosedPorch: 
3SsnPorch: 
ScreenPorch: 
PoolArea: 


normal : 
BsmtUnfSF: 
2ndFlrSF: 
WoodDeckSF: **

    
   

```{r}
hist(train_num$BsmtFinSF1)
hist(train_num$TotalBsmtSF)
hist(train_num$X1stFlrSF)
hist(train_num$GrLivArea)
hist(train_num$OpenPorchSF)
hist(train_num$WoodDeckSF)
```

```{r}
kurtosis(train_num$BsmtFinSF1)
kurtosis(train_num$TotalBsmtSF)
kurtosis(train_num$X1stFlrSF)
kurtosis(train_num$GrLivArea)
kurtosis(train_num$OpenPorchSF)
```


```{r}
skewness(train_num$BsmtFinSF1)
skewness(train_num$TotalBsmtSF)
skewness(train_num$X1stFlrSF)
skewness(train_num$GrLivArea)
skewness(train_num$OpenPorchSF)
skewness(train_num$WoodDeckSF)
```
#Standardizing Normally Distributed Columns

```{r}
library(standardize)
library(clusterSim)
```

```{r}
data.Normalization(train_num$BsmtFinSF1,type = "n1",normalization="column")->train_num$BsmtFinSF1

data.Normalization(train_num$TotalBsmtSF,type = "n1",normalization="column")->train_num$TotalBsmtSF

data.Normalization(train_num$X1stFlrSF,type = "n1",normalization="column")->train_num$X1stFlrSF

data.Normalization(train_num$GrLivArea,type = "n1",normalization="column")->train_num$GrLivArea

data.Normalization(train_num$OpenPorchSF,type = "n1",normalization="column")->train_num$OpenPorchSF

data.Normalization(train_num$WoodDeckSF,type = "n1",normalization="column")->train_num$WoodDeckSF

data.Normalization(train_num$BsmtUnfSF,type = "n1",normalization="column")->train_num$BsmtUnfSF

data.Normalization(train_num$X2ndFlrSF,type = "n1",normalization="column")->train_num$X2ndFlrSF

data.Normalization(train_num$LotFrontage,type = "n1",normalization="column")->train_num$LotFrontage

data.Normalization(train_num$MasVnrArea,type = "n1",normalization="column")->train_num$MasVnrArea

data.Normalization(train_num$GarageArea,type = "n1",normalization="column")->train_num$GarageArea

data.Normalization(train$GarageCars,type = "n1",normalization="column")->train_num$GarageCars



```

non:
BsmtFinSF2: 
LowQualFinSF:
EnclosedPorch: 
3SsnPorch: 
ScreenPorch: 
PoolArea: 

```{r}
data.Normalization(train_num$BsmtFinSF2,type = "n5",normalization="column")->train_num$BsmtFinSF2

data.Normalization(train_num$LowQualFinSF,type = "n5",normalization="column")->train_num$LowQualFinSF

data.Normalization(train_num$EnclosedPorch,type = "n5",normalization="column")->train_num$EnclosedPorch

data.Normalization(train_num$X3SsnPorch,type = "n5",normalization="column")->train_num$X3SsnPorch

data.Normalization(train_num$ScreenPorch,type = "n5",normalization="column")->train_num$ScreenPorch

data.Normalization(train_num$PoolArea,type = "n5",normalization="column")->train_num$PoolArea

data.Normalization(train_num$LotArea,type = "n5",normalization="column")->train_num$LotArea

data.Normalization(train_num$MiscVal,type = "n5",normalization="column")->train_num$MiscVal



```

```{r}
colnames(train_num)
```

```{r}
#Normalizing and Standardizing the data
sd(train_num$GarageCars)
skewness(train_num$GarageCars)
kurtosis(train_num$GarageCars)

```

```{r}
as.factor(train_num$MSSubClass)->train_num$MSSubClass
as.factor(train_num$OverallQual)->train_num$OverallQual
as.factor(train_num$OverallCond)->train_num$OverallCond
```

```{r}
data.frame(factors,train_num)->massaged_data
```

```{r}
set.seed(123)
boruta.train <- Boruta(SalePrice~., data = massaged_data, doTrace = 2,maxRuns=100)
```

```{r}
boruta.train$finalDecision
```

###Attributes to be deleted

Street
Utilities
LotConfig
Condition1
Condition2
RoofMatl
BsmtFinType2
ExterCond
Heating
SaleType
BsmtHalfBath
YrSold
MoSold
BsmtFinSF2
LowQualFinSF
X3SsnPorch
ScreenPorch
PoolArea
MiscVal

```{r}
rem = c("Street","Utilities","LotConfig","Condition1","Condition2","RoofMatl","BsmtFinType2","ExterCond","Heating","SaleType","BsmtHalfBath","YrSold","MoSold","BsmtFinSF2","LowQualFinSF","X3SsnPorch","ScreenPorch","PoolArea","MiscVal")
```

```{r}

names(massaged_data) %in% rem->res

vec = c()
k=0
for (i in 1:length(res)) {
if(res[i]==FALSE)
{
    k=k+1
  vec[k]=i
}
}
```

```{r}
data = massaged_data[,vec]
```

```{r}
write.csv(data,"C:/Users/SAROJ/Desktop/House Price/clean_data.csv",row.names = F)
```


